### 2014-06-02 writing/S'14 paper/discussion.tex
Incremental paper update.
Adding Monday morning results to paper.

1 Para

- capable of a geometric encoding of fundamentals of logic

- capable of capturing recursive structure up to a scale comparable to what's used in language, and of true recursion

- capable of learning functional word meanings given adequate data, frontiers: more complex cases

>>>>

Discussion to be filled in based on Monday's results.\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...

% TODO: One para of closing discussion.
% - Results strongly suggest that RNTNs can encode the basics of this logic. First such result.
% -- Decay over size in recursion results not ideal, but this kind of behavior may not be problematic since there is a practical bound on the length of natural language sentences.
% - Future work: 
% -- Harder problems
% --- Sentences with more types of structure: Transitive verbs, relative clauses, etc.
% -- More models
% --- BP-RNNs, conv-RNNs

### 2014-06-02 writing/S'14 paper/join.tex
Incremental paper update.
Adding Monday morning results to paper.

 A TODO-dimensional RNTN model tuned for the task was able to correctly label TODO \% of the derivable test examples, and TODO \% of the remaining examples. The simpler RNN model with the same number of dimensions was able to derive only TODO \% and TODO \%, respectively.

>>>>

We found that the RNTN model worked best with 11 dimensional vector representations for the 80 sets and a 90 dimensional feature vector for the classifier. This model was able to correctly label 99.3\% of the derivable test examples, and 99.1\% of the remaining examples. The simpler RNN model worked best with 11 and 75 dimensions, respectively, but was able to achieve accuracies of only 90.0\% and 87.\%, respectively.

Discussion to be filled in based on Monday's results.\\...\\...\\...\\...\\...\\...

% Points for discussion: 
% - Fairly simple interpretation: RNTN generalized, RNN didn't
% - Future work: Can this generalize to models with huge numbers of entities, or does this result depend on the examples reflecting a small model in any way? Can't exhaustively generate large models without getting \#s - need sampling.

### 2014-06-02 writing/S'14 paper/quantifiers.tex
Adding Monday morning results to paper.

This experiment replicates similar work described in \citet{bowman2013can}, but replaces the partially manually annotated data in that paper with data that is generated directly using the logical system that we hope to model, yielding results that we believe to be substantially more straightforward to interpret.

@@

% \subsection{Experiments and results}

@@

\begin{table}\small\centering
\begin{tabular}{|l|l|}\hline
\textbf{Training configuration} & \textbf{Test accuracy}\\\hline
\textsc{all split}	&	TODO\% \\\hline
\textsc{pair two/less-than-two}	&	TODO\% \\
\textsc{pair not-all/not-most}	&	TODO\% \\
\textsc{pair all/some}	&	TODO\% \\
\textsc{pair no/no}	&	TODO\% \\
\hline
\end{tabular}

\caption{Quantifier experiment performance.\label{resultstable}}
\end{table} % TODO: Replace

% \subsection{Discussion}

@@

To be filled in based on Monday's results.\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...

>>>>

This experiment replicates similar work described in \citet{bowman2013can}, which found that RNTNs can learn to reason well with quantifier meanings given sufficient training data. This paper replaces the partially manually annotated data in that paper with data that is generated directly using the logical system that we hope to model, yielding results that we believe to be substantially more straightforward to interpret.

@@

@@

\begin{table}\small\centering
\begin{tabular}{|l|lll|}\hline
\textbf{Data} & \textbf{Most frequent class*} & \textbf{TODO dim RNN} & \textbf{16 dim RNTN}\\\hline
\textsc{all split}	& 35.4\% &	TODO\%&	88.1\% \\\hline
\textsc{pair two/less-than-two}	& 59.8\% &	TODO\% &	92.4\% \\
\textsc{pair not-all/not-most}	&0\% &	   TODO\%  &	82.1\% \\
\textsc{pair all/some}	& 0\%& TODO\%  &	80.4\% \\
\textsc{pair no/no}	& 30.8\% &	TODO\% &	100\% \\
\hline
\end{tabular}

\caption{Quantifier experiment performance. *Most frequent class accuracy is measured against the most frequent class in the training data, \#.\label{resultstable}}
\end{table} % TODO: Replace

@@

Discussion to be filled in based on Monday's results.\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...

% Notes for discussion:
% - First effort to learn a logic, results somewhat unclear.
% -- No straightforward way to prove that there is enough information in the data to learn quantifier projecitivies in this setting
% - Perfect performance on no-no promising that the model is learning at least some structure

### 2014-06-02 writing/S'14 paper/recursion.tex
Adding Monday morning results to paper.

Recursive structure is a prominent  feature of natural language. Consider, for example, \ii{Alice said hello}, \ii{Bob said that Alice said hello}, and \ii{Carl thinks that Bob said that Alice said hello}. Overt recursion of this kind is easy to find, and theoretical accounts of natural language syntax and semantics rely heavily on recursive structures.
In order for a model to be able to accurately learn natural language meanings, then, we expect that it would need to be able to learn to represent the meanings of function words in a such a way that they are able to behave correctly when taking their own outputs as input.

% Goal: Deep recursion!

@@

% TODO: Worth explicitly calling this project theorem proving? Yes! There was some confusion at CSLI.

@@

We deduplicate the data and discard pairs in which either statement is a tautology or contradiction (a statement that is true of either all or no possible assignments), for which none of the seven relation labels can accurately apply. We then divide the generated pairs into size bins based on the number of logical operators (\ii{and}, \ii{or}, or \ii{not}) in the larger of the two pairs being compared, and discard examples of size greater than twelve by this measure. Finally, we randomly sample 15\% of each bin for a held out test set.
...
65k train

 compute the relaitons between them, discard  , and consist of about 248k training examples and 44k test examples.

 Each of the six symbols and each of the three operators is treated as a word for the purposes of our model, and is represented by a randomly initialized vector representation.

...

% TODO: Add figure for results

train up to depth 5
test up to depth 12

% Describe data

\begin{figure}[t]
\begin{center}
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
...\\
\end{center}

\caption{Model performance by expression size. The vertical dashed line indicates the size of the largest expressions included in the training data.  \label{prop-figure}} 
\end{figure}

The RNN model was approximately optimal with N dimensional word representations and an M dimensional comparison layer. The RNTN was approximately optimal with N and M dimensions, respectively.

% TODO: Include dimensionality

>>>>

Recursive structure is a prominent  feature of natural language. Consider, for example, \ii{Alice said hello}, \ii{Bob said that Alice said hello}, and \ii{Carl thinks that Bob said that Alice said hello}. Overt recursion of this kind is easy to find, and theoretical accounts of natural language syntax and semantics rely heavily on recursive structures. In order for a model to be able to accurately learn natural language meanings, then, we expect that it would need to be able to learn to represent the meanings of function words in a such a way that they are able to behave correctly when taking their own outputs as input. In evaluating the model, we take advantage of the fact that recursive structures of this kind define potentially infinite languages by testing the model on strings that are longer and more complex than any seen in testing.

@@

% NOTE: Worth explicitly calling this project theorem proving? Yes! There was some confusion at CSLI.

@@

We deduplicate the data and discard pairs in which either statement is a tautology or contradiction (a statement that is true of either all or no possible assignments), for which none of the seven relation labels can accurately apply. We then divide the generated pairs into size bins based on the number of logical operators (\ii{and}, \ii{or}, or \ii{not}) in the larger of the two pairs being compared, and discard examples of size greater than twelve by this measure. Finally, we randomly sample 15\% of each bin for a held out test set.

We trained both the RNN and RNTN models on the data of size four or less (65k pairs), and tested it on examples of up to size 12 (44k pairs). We initialized the model parameters randomly, including the vector representations of the six variables.

The results are shown in Figure \ref{prop-results}. In tuning, we found that the RNN model was approximately optimal with 45 dimensional vector representations, and the RNTN model was approximately optimal with 25 dimensions. We fixed the size of the feature vector for the classifier at 75 dimensions. We found that the RNTN model was able to perform almost perfectly on unseen small test examples, with accuracy above 99\% below size four. After depth four, performance gradually falls with increasing size. The RNN model did not perform well, reaching only 88.2\% accuracy on the smallest test examples, and declining from there to near-baseline performance at size 12.

\begin{figure}[t]
\begin{center}
\includegraphics[width=5.5in]{recursion\string_results.eps}
\end{center}

\caption{Model performance by expression size.  \label{prop-results}} 
\end{figure}

Discussion to be filled in based on Monday's results.\\...\\...\\...\\...\\...\\...\\...\\...\\...\\...

% TODO:
% Points for discussion
% - The RNTN has learned to approximate the correct funtionn
% -- The error introduced by the approximation likely grows with depth, but is sufficiently small at the training example sizes

% - The RNN has plausibly learned an approximation as well, but one which is quite noisy even without recursion
% -- Possible but unlikely that further tuning and different types or amounts of training data could get the RNN to work

% - Future work:
% -- Generate much larger examples to tease apart the ability of the model to approximate a representable function from data, and the ability of the model to represent
